\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-08 journalWallFriction/Experiment.tex
A bunch of figures and texts added!

To demonstrate Alg.~\ref{alg:optimalAlg} experimentally, we performed several tests.
Each used the same magnetic setup shown in Fig.~\ref{fig:}.
% The figure might need to be referenced 
 Two different intestine models were employed, the first a 3D-printed cross-section representation of a small intestine, and the second a cross-section of a bovine stomach.

@@

To obtain experimental data, the test samples which comprised of the phantom intestine model and the bovine cross section, were placed in laser cut acrylic discs and then immersed in corn syrup. Corn syrup was used to have the best viscosity(12000 cP) for the experiments. The velocities of particles immersed in it were dampened enough to control their movements with ease. Spherical $\SI{0.5}{\milli\metre}$ magnets (supermagnetman \#SP0100-50) were used as our particles.

>>>>

To demonstrate Alg.~\ref{alg:optimalAlg} experimentally, we performed several tests.
Each used the same magnetic setup shown in Fig.~\ref{fig:IntroPic}.
% The figure might need to be referenced 
 Two different intestine models were employed, the first a 3D-printed cross-section representation of a small intestine, and the second a cross-section of a bovine stomach.

@@

To obtain experimental data, the test samples which comprised of the phantom intestine model and the bovine cross section, were placed in laser cut acrylic discs and then immersed in corn syrup. Corn syrup was used to have the best viscosity(12000 cP) for the experiments. The velocities of particles immersed in it were dampened enough to control their movements with ease. Spherical $\SI{1}{\milli\metre}$ magnets (supermagnetman \#SP0100-50) were used as our particles.

### 2018-05-08 journalWallFriction/simulation.tex
A bunch of figures and texts added!

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{numcontour.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{distcontour.pdf}\end{overpic}
 \vspace{-2em}
\caption{\label{fig:contour}
Plots showing the algorithm with one goal on the boundary.
}
\end{figure}

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{deltanum.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{deltadist.pdf}\end{overpic}
\caption{\label{fig:deltanumdist}
Plots showing decreasing error as the number of moves grows.
} 
\vspace{-1em}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{numcontour.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{distcontour.pdf}\end{overpic}
 \vspace{-2em}
\caption{\label{fig:contour}
Plots show performance with one goal on the boundary.
}
\end{figure}

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{deltanum.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{deltadist.pdf}\end{overpic}
\caption{\label{fig:deltanumdist}
Particle swap poles as their goal is the worst case. It can never be achieved but can be asymptotically reached. Plots show decreasing error as the number of moves grows.
} 
\vspace{-1em}
\end{figure}

### 2018-05-08 journalWallFriction/theory.tex
A bunch of figures and texts added!

 If the goal configuration can be reached in three moves, the shortest path has a simple solution. The first move makes one particle hit a wall, the second move adjusts the relative spacing error  to zero, and  the third move takes the particles to their final positions. 
The second move cannot be shortened, so optimization depends on choosing the location where the particle hits the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal hit location, as shown in Fig. \ref{fig:reflection}. There are four walls, and four candidate solutions.

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{Reflection.pdf}\end{overpic}
\caption{\label{fig:reflection}
The shortest path between two points in a square. Reflecting the goal position across the boundary wall and plotting a straight line gives the shortest path.
} \vspace{-1em}
\end{figure}

>>>>

 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle hit a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final positions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle hits the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal hit location, as shown in Fig. \ref{fig:reflection}. There are four walls, and four candidate solutions.

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{Reflection.pdf}\end{overpic}
\caption{\label{fig:reflection}
The shortest ?three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle.
} \vspace{-1em}
\end{figure}

### 2018-05-08 journalWallFriction/theory2robAlgs.tex
A bunch of figures and texts added!

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 hits the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(right) Similarly, if particle 2 hits the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
}
\end{figure}
If a particle is touching a wall, the other particle can move freely in the reachable set as shown in Fig.~\ref{fig:TwoRegions}.
Alg.~\ref{alg:polygonReachbale} computes the reachable set for any convex workspace.
 Fig.~\ref{fig:polygonAlg} illustrates the procedure to construct the reachable set generated by collisions with the $i^{th}$ side. If one particle hits side $i$ before the other ($\overline{ s_1s_2 }\nparallel \overline{ p_i p_{i+1}} $), the reachable set is defined by a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the reachable set of $\Delta$ configurations.
 % by computing the reachable set for all the sides of the polygon. Fig.~\ref{fig:polygonAlg} shows different cases with the particles and an arbitrary side. If particle 2 is touching the $i^{th}$ side, we compute if particle 1 will stay in the polygon or not. Then we generate the reachable set using all the vertices of the polygon and potential place of particle 1. We unify all the reachable sets corresponding to all the sides. Alg.~\ref{alg:polygonReachbale} computes reachable set for any convex polygonal workspace. 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i p_{i+1}}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

A circle has an infinite number of sides, thus infinite reachable sets. However, the reachable set can be parameterized by the angle of first contact location $\psi$, as shown in Fig.~\ref{fig:regionMove} where 
%We make the reachable sets by knowing the angle of the chord, $\psi$, shown in Fig.~\ref{fig:psigamma}. Minimum and maximum values of $\psi$ can be calculated in the following equation.
\begin{align}
 \psi \in [\psi_{\min}, \psi_{\max}]= \theta + \Big[\frac{\sin^{-1}{d}}{2r} - \frac{\pi}{2},  \frac{\pi}{2} -\frac{\sin^{-1}{d}}{2r} \Big].
% \psi_{\max} &= \theta -\frac{\alpha}{2} + \frac{\pi}{2}
\end{align}
The possible first contact locations are on an arc with interior angle $\gamma$ parameterized by $\psi$:
\begin{align}\label{eq:gamma}
\gamma(\psi) &= \cos^{-1} \Big(1-\frac{d_\perp(\psi)}{r} \Big), \textrm{ where:}\\ \label{eq:dprep}
d_\perp(\psi)&= 2 ||(s_1.p_\psi(\psi) - s_2.p_\psi(\psi))||,\\ \label{eq:ppsi}
p_\psi(\psi) &= r[\cos(\psi ), \sin(\psi )].
\end{align} 
Reachable sets with $\pi$ difference in $\psi$ value are equivalent in the  $\Delta$ configuration space, so we can plan in this space and choose between the two options to immobilize the particle closest to a wall. 
The reachable $\Delta$ configuration set for any first contact point defined by $\psi$ is the area under a chord from angle $\psi- \frac{\gamma(\psi)}{2}$ to $\psi+ \frac{\gamma(\psi)}{2}$, for a circle of radius $r$ centered at $c = r(\cos(\psi-\pi), \sin(\psi-\pi))$. One such chord is drawn in red in Fig.~\ref{fig:regionMove}.

The equations for the four lines outlining the union of reachable $\Delta$ configuration sets are as follows:
\begin{align}\label{eq:circlereachable}
l_1 =  r \Big(&(\cos\psi_{\min}- \cos(\gamma + \psi_{\min}) )\\ \nonumber
 + &(\sin\psi_{\min}- \sin(\gamma + \psi_{\min}))\Big) &  0<\gamma< \gamma(\psi_{\min}),\\ \nonumber
l_2 =  r \Big(&(\cos\psi_{\max}- \cos(\gamma + \psi_{\max}))\\ \nonumber
 + &(\sin\psi_{\max}- \sin(\gamma + \psi_{\max}))\Big) &  \gamma(\psi_{\max})<\gamma< 0,\\  \nonumber
l_3 =  r \Big(&(\cos\psi- \cos( \psi+\gamma(\psi) ) )\\ \nonumber
+ &( \sin\psi-\sin( \psi+ \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max},\\ \nonumber
l_4 =  r \Big(&(\cos\psi- \cos( \psi-\gamma(\psi) ))\\ \nonumber
+ & ( \sin\psi- \sin( \psi- \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max}.\\ \nonumber
\end{align}
We combine these boundaries to compute the reachable set summarized in Alg.~\ref{alg:circularReachbale}.
Next, find a $\psi$ that would enable us to reach $\Delta g_c$, the nearest point in the reachable set to $\Delta g$. %Eq.~\eqref{eq:ifinchord} checks if an arbitrary point $p$, is in the reachable set corresponding to $\psi$.
We first check if $\Delta g_c$ is in the $\Delta$ configuration space chords defined by either $\psi_{\min}$ or $\psi_{\max}$ using \ref{eq:ifinchord}.

\begin{align}\label{eq:ifinchord}
&(\Delta g_c.x - c.x)^2 + (\Delta g_c.y - c.y)^2  > r^2 \wedge\\ \nonumber
 &( c.x-\Delta g_c.x ) \cos\psi + ( c.y-\Delta g_c.y) \sin\psi > r\cdot \cos\gamma.
\end{align}

%Here $c$ is the coordinate of the workspace center and $r$ is the radius of the workspace.
%We first check if $\Delta g_c$ is achievable with $\psi_{min}$ and $\psi_{max}$.
 If $\Delta g_c$ is not in either chord, we draw a line from $\Delta g_c$ to the current relative position, $\Delta p$. This line is a chord of the circle centered at $c$. The $\psi$ to this chord obeys:
  \begin{equation}
 \psi = \tan^{-1}(\Delta p - \Delta g_c ).
 \end{equation}

The particles achieve $\Delta g_c$ in two moves. The first move causes one particle to touch the wall, the second move achieves the required relative position.

>>>>

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 hits the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(right) Similarly, if particle 2 hits the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
}
\end{figure}
If a particle is touching a wall, the other particle can move freely in the reachable set as shown in Fig.~\ref{fig:TwoRegions}.
Alg.~\ref{alg:polygonReachbale} computes the reachable set for any convex workspace.
 Fig.~\ref{fig:polygonAlg} illustrates the procedure to construct the reachable set generated by collisions with the $i^{\textrm{th}}$ side. If one particle hits side $i$ before the other ($\overline{ s_1s_2 }\nparallel \overline{ p_i p_{i+1}} $), the reachable set is defined by a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the reachable set of $\Delta$ configurations.
 % by computing the reachable set for all the sides of the polygon. Fig.~\ref{fig:polygonAlg} shows different cases with the particles and an arbitrary side. If particle 2 is touching the $i^{th}$ side, we compute if particle 1 will stay in the polygon or not. Then we generate the reachable set using all the vertices of the polygon and potential place of particle 1. We unify all the reachable sets corresponding to all the sides. Alg.~\ref{alg:polygonReachbale} computes reachable set for any convex polygonal workspace. 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i p_{i+1}}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

A circle has an infinite number of sides, thus infinite reachable sets. However, the reachable set can be parameterized by the angle of first contact location $\psi$, as shown in Fig.~\ref{fig:regionMove} where 
%We make the reachable sets by knowing the angle of the chord, $\psi$, shown in Fig.~\ref{fig:psigamma}. Minimum and maximum values of $\psi$ can be calculated in the following equation.
\begin{align}
 \psi \in [\psi_{\min}, \psi_{\max}]= \theta + \Big[\frac{\sin^{-1}{d}}{2r} - \frac{\pi}{2},  \frac{\pi}{2} -\frac{\sin^{-1}{d}}{2r} \Big].
% \psi_{\max} &= \theta -\frac{\alpha}{2} + \frac{\pi}{2}
\end{align}
The possible first contact locations are on an arc with interior angle $\gamma$ parameterized by $\psi$:
\begin{align}\label{eq:gamma}
\gamma(\psi) &= \cos^{-1} \Big(1-\frac{d_\perp(\psi)}{r} \Big), \textrm{ where:}\\ \label{eq:dprep}
d_\perp(\psi)&= 2 ||s_1.p_\psi(\psi) - s_2.p_\psi(\psi)||,\\ \label{eq:ppsi}
p_\psi(\psi) &= r[\cos(\psi ), \sin(\psi )].
\end{align} 
Reachable sets with $\pi$ difference in $\psi$ value are equivalent in the  $\Delta$ configuration space, so we can plan in this space and choose between the two options to immobilize the particle closest to a wall. 
The reachable $\Delta$ configuration set for any first contact point defined by $\psi$ is the area under a chord from angle $\psi- \frac{\gamma(\psi)}{2}$ to $\psi+ \frac{\gamma(\psi)}{2}$, for a circle of radius $r$ centered at $c = r(\cos(\psi-\pi), \sin(\psi-\pi))$. One such chord is drawn in red in Fig.~\ref{fig:regionMove}.

The equations for the four lines outlining the union of reachable $\Delta$ configuration sets are as follows:
\begin{align}\label{eq:circlereachable}
l_1 =  r \Big(&(\cos\psi_{\min}- \cos(\gamma + \psi_{\min}) )\\ \nonumber
 + &(\sin\psi_{\min}- \sin(\gamma + \psi_{\min}))\Big) &  0<\gamma< \gamma(\psi_{\min}),\\ \nonumber
l_2 =  r \Big(&(\cos\psi_{\max}- \cos(\gamma + \psi_{\max}))\\ \nonumber
 + &(\sin\psi_{\max}- \sin(\gamma + \psi_{\max}))\Big) &  \gamma(\psi_{\max})<\gamma< 0,\\  \nonumber
l_3 =  r \Big(&(\cos\psi- \cos( \psi+\gamma(\psi) ) )\\ \nonumber
+ &( \sin\psi-\sin( \psi+ \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max},\\ \nonumber
l_4 =  r \Big(&(\cos\psi- \cos( \psi-\gamma(\psi) ))\\ \nonumber
+ & ( \sin\psi- \sin( \psi- \gamma(\psi)))\Big) &  \psi_{\min}<\psi< \psi_{\max}.\\ \nonumber
\end{align}
We combine these boundaries to compute the reachable set summarized in Alg.~\ref{alg:circularReachbale}.
Next, find a $\psi$ that would enable us to reach $\Delta g_c$, the nearest point in the reachable set to $\Delta g$. %Eq.~\eqref{eq:ifinchord} checks if an arbitrary point $p$, is in the reachable set corresponding to $\psi$.
We first check if $\Delta g_c$ is in the $\Delta$ configuration space chords defined by either $\psi_{\min}$ or $\psi_{\max}$ using:

\begin{align}\label{eq:ifinchord}
&(\Delta g_c.x - c.x)^2 + (\Delta g_c.y - c.y)^2  > r^2 \textrm{     \textbf{and}}\\ \nonumber
 &( c.x-\Delta g_c.x ) \cos\psi + ( c.y-\Delta g_c.y) \sin\psi > r\cos\gamma.
\end{align}

%Here $c$ is the coordinate of the workspace center and $r$ is the radius of the workspace.
%We first check if $\Delta g_c$ is achievable with $\psi_{min}$ and $\psi_{max}$.
 If $\Delta g_c$ is not in either chord, we draw a line from $\Delta g_c$ to the current relative position, $\Delta p$. This line is a chord of the circle centered at $c$. The $\psi$ to this chord obeys:
  \begin{equation}
 \psi = \tan^{-1}\Big(\frac{\Delta p.x - \Delta g_c.x}{\Delta p.y - \Delta g_c.y} \Big).
 \end{equation}

The particles achieve $\Delta g_c$ in two moves. The first move causes one particle to touch the wall at $p_\psi$, \eqref{eq:ppsi}. The second move achieves the required relative position.
